---
title: "E-Commerce Analysis Google Store"
author: "Francesca Monte"
date: "2026-03-05"
output: html_document
---

```{r setup, message=FALSE}
# install packages
install.packages("tidyverse")
install.packages("janitor")
install.packages("skimr")
# download packages
library(tidyverse)
library(janitor)
library(skimr)

# download data 
df_google <- read_csv("google_analytics_data.csv")

# clean column names
df_google <- df_google %>% 
  clean_names()

# let's start initial screening
df_google %>% skim_without_charts()

```{r pulizia}
df_final <- df_google %>%
  
# Transforming null values (na) in zeros to make calculations
  mutate(revenue_usd = replace_na(revenue_usd, 0),
         transactions = replace_na(transactions, 0)) %>%
  
# Creating a column that instantly tells if a user is a "Buyer"
  mutate(is_buyer = transactions > 0)

# Let's verify the result
df_final %>% 
  group_by(is_buyer) %>% 
  summarise(conteggio = n(), incasso_totale = sum(revenue_usd))

```{r grafico_browser}
# Creating a dataset summary for the chart
browser_analysis <- df_final %>%
  filter(is_buyer == TRUE) %>%       # analysing only those who actually bought something
  group_by(browser) %>%
  summarise(totale_revenue = sum(revenue_usd)) %>%
  arrange(desc(totale_revenue)) %>%
  slice_max(totale_revenue, n = 5)   # keeping just the first 5 browser to avoid chart confusion

# first chart
ggplot(data = browser_analysis) +
  geom_col(mapping = aes(x = reorder(browser, totale_revenue), y = totale_revenue), fill = "steelblue") +
  coord_flip() +    # rotating the chart to read browser names better
  labs(title = "Top 5 Browser per Total Revenue",
       subtitle = "Data from Google Merchandise Store",
       x = "Browser",
       y = "Total revenue (USD)") +
  theme_minimal()   # clean elegant theme




```

### Conclusions on Browser Analysis

The revenue analysis shows a huge domination of **Chrome**. 
Even though Safari and Firefox contributes to traffic volume, their revenue is marginal. 
This suggests a strong correlation between the Google ecosystem and the propension to buy from it in their official store.


